---
title: "Getting started with netfs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with netfs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(netfs)
```

## Local filesystem operations

With no connection, netfs delegates directly to `fs`.

```{r}
dir_ls(tempdir())
file_exists(tempdir())
```

## Connection objects

Constructors validate configuration without opening a connection. Passwords
are stored through `keyring` and are not retained in connection objects.

```{r, eval=FALSE}
server <- ftp("ftp.example.org", user = "analyst")
set_creds(server)
```

Set `NETFS_KEYRING` in `.Renviron` to select a named keyring. Do not store the
password itself in `.Renviron`.

## SSH

```{r, eval=FALSE}
server <- ssh("server.example.org", user = "user")
dir_ls("/data", con = server)
```

## FTP

```{r, eval=FALSE}
server <- ftp("ftp.example.org", user = "user")
file_info("/data/input.csv", con = server)
```

## SMB

```{r, eval=FALSE}
server <- smb("fileserver", "DATA", user = "user")
dir_ls("/2026", con = server)
```

## Uploading and downloading files

`file_download()` copies from remote to local. `file_upload()` copies in the
other direction. Both protect existing destinations unless `overwrite = TRUE`.

`file_transfer()` copies between two remote connections through a temporary
local staging file. It preserves the source and removes the temporary file
after success or failure.

```{r, eval=FALSE}
file_transfer(
  "/incoming/report.csv",
  "/archive/",
  from = ftp_server,
  to = smb_server
)
```

## Backend capabilities

```{r}
netfs_capabilities()
```

## Error handling

Remote failures inherit from `netfs_error`; specific subclasses distinguish
authentication, missing paths, unavailable clients, timeouts, and unsupported
operations.
